\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-06-08 paper/ms.tex
starting on performance section

@@

\begin{figure}[tp]
\begin{center}
\includegraphics[width=\textwidth]{figures/benchmark_darwin.pdf}
\caption{\dfmtodo{Cholesky} A benchmark showing the computational scaling of \celerite\ using the
    \texttt{vanilla} band solver as a function of the number of data points
    and the number of terms.
    \emph{(left)} The cost of computing \eq{gp-likelihood} with a covariance
    matrix given by \eq{celerite-kernel} as a function of the number of data
    points $N$.
    The different lines show the cost for different numbers of terms $J$
    increasing from bottom to top.
    To guide the eye, the straight black line without points
    shows linear scaling in $N$.
    \emph{(right)} The same information plotted as a function of $J$ for
    different values of $N$.
    Each line shows the scaling for a specific value of $N$ increasing from
    bottom to top.
    The black line shows quadratic scaling in $J$.
    \figurelabel{benchmark}}
\end{center}
\end{figure}

>>>>

\subsection{Performance}

We have derived a novel method for computing the Cholesky factorization of the
covariance matrices produced by \celeriteterm\ models.
In this section, we demonstrate the scalability and numerical performance of
this algorithm.

\begin{figure}[tp]
\begin{center}
\includegraphics[width=\textwidth]{figures/benchmark_darwin.pdf}
\caption{A benchmark showing the computational scaling of \celerite\ using the
    Cholesky factorization routine for rank-$2\,J$ semiseparable matrices as
    described in the text.
    \emph{(left)} The cost of computing \eq{gp-likelihood} with a covariance
    matrix given by \eq{celerite-kernel} as a function of the number of data
    points $N$.
    The different lines show the cost for different numbers of terms $J$
    increasing from bottom to top.
    To guide the eye, the straight black line without points
    shows linear scaling in $N$.
    For comparison, the computational cost for the same model using a general
    Cholesky factorization routine implemented in the Intel MKL linear algebra
    package.
    \emph{(right)} The same information plotted as a function of $J$ for
    different values of $N$.
    Each line shows the scaling for a specific value of $N$ increasing from
    bottom to top.
    The black line shows quadratic scaling in $J$.
    \figurelabel{benchmark}}
\end{center}
\end{figure}

@@
